### 2022-01-02 intro.tex
writing more stuff

Most of the large literature concerning \acp{NCS}, however, follows a theoretical approach, and only a small fraction of it deals with experimental studies.
The inherent inter-domain nature of \acp{NCS}, which intertwines knowledge from the fields of communications, computing, and control theory, coupled with the complexity of experimental platforms make these kinds of studies hard to perform.
Moreover, we identify a gap in knowledge pertaining to the reproducibility and comparison of experimental studies on these systems.
Existing experimental research includes a large variety of heterogeneous hardware and software platforms, as well as methodologies and \acp{KPI}.
In turn, this leads to hardware, software, and methodology fragmentation, as different studies tend to prefer approaches more favored in their respective communities.
Additionally, existing studies tend to focus on individual aspects and components of a system, thus producing results which do not provide a complete image of the \ac{NCS}.

The most straightforward approach to experimental research in \ac{NCS} use setups in which the complete system uses real hardware.
\cite{Drew2005NCSWLAN,Baumann2018LowPower} are examples of studies employing this approach.
\textcite{Drew2005NCSWLAN} present \iac{NCS} model which considers both random packet delay and loss on both the sensor and actuator sides of the feedback loop; \textcite{Baumann2018LowPower}, on the other hand, develop an evaluation methodology for wireless \ac{NCS}.
Both works validate their results on physical testbeds, consisting of inverted penduli plants controlled wirelessly over WiFi from a central computation point.
\todo[inline]{More examples?}

Other

>>>>

Most of the large literature concerning \acp{NCS}, however, follows a theoretical approach, and only a small fraction of it deals with experimental studies.
The inherent inter-domain nature of \acp{NCS}, which intertwines knowledge from the fields of communications, computing, and control theory, coupled with the complexity of experimental platforms make these kinds of studies hard to perform.
Moreover, we identify a gap in knowledge pertaining to the reproducibility and comparison of experimental studies on these systems.
Existing experimental research includes a large variety of heterogeneous hardware and software platforms, as well as methodologies and \acp{KPI}.
In turn, this leads to hardware, software, and methodology fragmentation, as different studies tend to prefer approaches more favored in their respective communities.
Furthermore, existing studies tend to focus on individual aspects and components of a system, thus producing results which do not provide a complete image of the \ac{NCS}.

The most straightforward approach to experimental research in \ac{NCS} use setups in which the complete system uses real hardware.
\textcite{Drew2005NCSWLAN} present \iac{NCS} model which considers both random packet delay and loss on both the sensor and actuator sides of the feedback loop; \textcite{Baumann2018LowPower}, on the other hand, develop an evaluation methodology for wireless \ac{NCS}.
Both works validate their results on physical testbeds, consisting of inverted penduli plants controlled wirelessly over WiFi from a central computation point.
Similarly, \textcite{Li2014Wireless} implement a wireless microcontroller-based system for vibration control and validate it on a physical prototype consisting of a cantilever beam controlled over a IEEE 802.15.4 \ac{WPAN} system.

Conversely, some studies choose to instead use completely \emph{simulated} \ac{NCS} setups~\cite{Andersson2005Simulation,Eyisi2012NCSWT}.
Such an approach is employed by \textcite{Du2009Smith}; the authors develop a novel \emph{Smith} predictor to compensate for varying latencies in wireless \acp{NCS} and validate it using the \emph{TrueTime}~\cite{Henriksson2002TrueTime} simulator.
In \textcite{Chen2015synccontrol} the authors validate and evaluate a number of synchronous control strategies for three-motor setups using completely simulated \acp{NCS} environments.
\citeauthor{Wu2012NPC} introduce the concept of \emph{network predictive control} in\ \cite{Wu2012NPC} and use it to balance a simulated inverted pendulum over a simulated wireless network.

Finally, a number of experimental studies instead employ hardware- and network-in-the-loop approaches.
Hardware-in-the-loop refers to \ac{NCS} setups in which a real control system interacts with an emulated network.
Such setups have been used by studies
